\newpage
\section*{Snags}

\subsection*{Overall}

\begin{itemize}
\item[ALL:]
Confirm individuals to add to the participant portal.
\item[ALL:]
Check partner details in the participant portal and modify if necessary.
\item[KH:]
Update project summary in participant portal.
\item[ALL:]
Check budget in participant portal.
\item[VJ/KH:]
Trim to 70 pages.
\end{itemize}

\subsection*{Section 1}

\begin{itemize}
\item[CODEPLAY:]
Add background for TensorC use case in the background section
\item[ALL:]
Update Innovation potential (1.4.11).  Talks too much about C++, needs to be focused around model-based development, 
software defined infrastructure, maybe multicore.
Codeplay added paragraph on innovation potential; search for CODEPLAY:
\item[-] - sec.1.4.10 key tech updated by SG in PharosN section 
\end{itemize}


\subsection*{Section 2}
\begin{itemize}
\item[ALL:]
Update measures to maximise impact (2.3).  Move away from purely C++ towards model-based development, SDI etc.
\item[ALL, esp IBM:]
Check and update exploitation plans. (2.3.1)
\item[-] - sec.2.3.1 sec Standardisation Committees:  GOLEM ref added by SG
\item[-] - sec.2.3.1 sec Draft Exploitation Plan for GOLEM updated by SG \item[-] - sec.2.3.1 sec Draft Exploitation Plan for JPOIC introduced by SG

\item[ALL:]
Add relevant conferences and journals.  (2.3)
\item[-] SCCH - done
\item[ALL:]
Provide information on relevant expert working groups, standards organisations etc. that you are members of.  (2.3)
\item[ALL:]
Confirm that you are happy with the section on Knowledge Management (2.3.3)\item[-] - OK by SG
\item[-] - sec.2.3.4 sec  Note re dissemination in ITU added by SG
\item[-] OK by SCCH.
\end{itemize}

\subsection*{Section 3}
\begin{itemize}
\item[ALL:]
Check Gantt Chart (p. 32)
\item[VJ:]
The  workplan in the GANTT looks like a waterfall, with too even divisions by year boundary.  Modelling tasks are probably
too late and all tasks extend into year 3.  Do requirements only flow into use cases? Should there be some early feedback
from evaluation?  All tasks have precisely three parts: this is strange.
\item[VJ:]
Do we have too many tasks?
\item[for VJ by SG:] Note the separation of Use Case tasks into T7.3 and T7.4 ! In addtion the question is if the T7.4 shall be further split into two separate tasks for TensorC (CODE) and ADAS (PRL)? If yes, who  will be the partners? Then it shall be further reflected in the Gantt   
\item[VJ:]
deliverables.tex has not been completed?  Most deliverables are not yet defined.
\item[VJ:]
Check the consistency of Deliverables table (p. 34)
\item[-] checked by SCCH (WP5)
\item[VJ:]
Remove security standards from the list of milestones and replace with 'compliance to security/safety standards'
\item[ALL:]
Add 2-3 critical risks per WP to the Critical Risks table (p. 56)
\item[-] - critical risks added by SG in relation to WP7 
\item[-] critical risks added with respect to WP5 (SCCH)
\item[-] check modification of related WP \# in the risks added by Codeplay.
\item[VJ:]
Complete table 4
\item[VJ:]
Update Committees and Boards (p. 57)
\item[ALL:]
Update table of Principal Investigators (p. 58)
\item[-] - updated by SG 
\item[-] updated by SCCH
\item[VJ:]
Update Areas of Expertise and diagram (p. 59)
\item[-] - updated by SG (VJ: edit/modify if necessary)
\item[ALL:]
Check the Additional Partner Costs (p. 60)
\item \item[-] - updated by SG (VJ: edit/modify if necessary)
\end{itemize}




\subsection*{Section 4}
\begin{itemize}
\item[ALL:]
Check partner description and update with new projects, publications etc.
\item[-] - GOLEM and JMOIC profiles were updated by SG
\end{itemize}

\subsection*{Section 5}

\begin{itemize}
\item[ALL:]
Confirm that there are no ethical issues (e.g. with JMOIC data).
\item \item[-] - no issues for JMOIC
\end{itemize}

\newpage
\section*{Snags completed}

\subsection*{Overall}

\begin{itemize}
\item[KH/VJ:]
Change project title and acronym.
\item[KH:]
Set up participant portal.  
\item[KH:]
Enter agreed budgets in participant portal.
\end{itemize}

\subsection*{Section 1}

\begin{itemize}
\item[] description of figure 2 in 1.3.2 does not match the new picture
\item[IBM, INRIA, PRL, SCCH:]
Check positioning and include TRLs for tools (1.3.3).
\item[-] - sec.1.3.3 updated re GOLEM TRL by SG
\item[-] - sec. 1.3.3 updated by SCCH
\item[ALL:]
Update project list (1.3.4).
\item[-] - sec.1.3.4 updated re GOLEM by SG
\item[-] - sec. 1.3.4 updated by SCCH
\item[SCCH:]
Finish Section 1.3.2, add diagram of interaction between runtime system, modelling and optimisation and write some text about it (DONE)
\item[-] done (some questions remain in connection with the main diagram)
\item[INRIA:]
Complete 1.4.2
\item[AGH:]
Complete 1.4.3 - (done)
\item[USTAN:]
Complete 1.4.4
\item[CODEPLAY:]
Complete 1.4.5 (can be considered done)
\item[SCCH:]
Complete 1.4.6 - (done)
\item[IBM:]
Complete 1.4.7
\item[GOLEM:]
Complete 1.4.8
\item[-] - sec.1.4.8 was updated by SG 10.04.2018
\item[VJ:]
Increase size of Figure 1.
\item[?:]
Fill in XX as appropriate..
\item[KH:]
Add JMOIC as a partner (p.1)?
\item[VJ:]
Update which new aims are fulfilled by each objective.
\item[KH:]
Add positioning (1.3.3). Note: Needs checking and updating.
\item[SCCH:]
Finish Section 1.3.2, add diagram of interaction between runtime system, modelling and optimisation and write some text about it
\end{itemize}

\subsection*{Section 2}

\begin{itemize}
\item[VJ:]
Add Expected Impacts (2.1).
\item[VJ:]
Update improving innovation capacity (2.1).
\item[VJ:]
Update societal impacts (2.1).
\item[VJ:]
Add barriers to achieving impacts (2.1).
\item[ALL:]
Update measures to maximise impact (2.3).  Move away from purely C++ towards model-based development, SDI etc.
\item[JMOIC:]
Add draft exploitation plan. (2.3.1) - Done! 
\item[CODE:]
Add draft exploitation plan. (2.3.1)   (done)
\item[AGH:]
Add draft exploitation plan. (2.3.1) (done) 
item[JMOIC:]
Add draft exploitation plan. (2.3.1) - Done! 
\item[CODE:]
Add draft exploitation plan. (2.3.1)   (done)
\item[AGH:]
Add draft exploitation plan. (2.3.1) (done) 
\end{itemize}

\subsection*{Section 3}

\begin{itemize}
\item[VJ:]
Update PMs, Start and End dates in WP List
\item[VJ:]
Add Pert Chart (p.31) -- DONE, VJ
\item[VJ:]
Add Success Criteria for Milestones table (p. 33)
\item[ALL:]
Add PMs to the WP headers/tasks
\item[-] - all WPs and its tasks were analysed and relevant PMs added by SG for GOLEM 
\item[VJ:]
Fix start and end dates for tasks in all WPs
\end{itemize}

\subsection*{Section 4}

\begin{itemize}
\item[CODE:]
Complete partner description. (done)
\item[AGH:]
Complete partner description. (done)
\item[JMOIC:]
Complete partner description.
\end{itemize}

\subsection*{Section 5}

\begin{itemize}
\item
\end{itemize}

\newpage
