\addtocounter{wpno}{1}

\begin{Workpackage}{\thewpno}
\wplabel{wp:management}
\WPTitle{\wpname{\thewpno}}
\WPStart{Month 1}
\WPParticipant{SA}{24}

\begin{WPObjectives}
The objectives of \theWP{} are to undertake all project management activities, including:
\begin{compactitem}
\item
monitoring the overall progress of the project;
\item
ensuring the timely production of deliverables and other project outputs;
\item
reporting to the European Commission on financial matters;
\item
preparing and attending the annual project review meetings; and

\item
managing the project Advisory Board.
\end{compactitem}
\end{WPObjectives}

\begin{WPDescription}
This workpackage will perform all the activities related to monitoring
of progress towards the project milestones shown on Page~\pageref{sect:milestones}
and the deliverables listed on Page~\pageref{sect:deliverables},
assuring the quality of the deliverables, ensuring the
collation and distribution of the required periodic and other reports,
questionnaires and deliverables to
the European Commission, arranging project management meetings, tracking
the project budget in terms of expenditure and person-months,
obtaining financial certificates as required, convening project
management meetings, ensuring that important project documents
such as the project contract and the consortium agreement are
properly maintained and amended as necessary, ensuring that
contractual details are complied with, preparing any necessary amendment requests,
preparing for the periodic review meetings, and reviewing the research
results against the aims and objectives of the project.
It also involves managing and supporting the project
Advisory Board, including supporting attendance at project
meetings and obtaining feedback on the project direction and
results.
\end{WPDescription}

\begin{WPDeliverables}
\begin{compactitem}
\item
\ref{mgt:mailinglists}
(Month 1): 
Internal and external mailing lists.
\item
\ref{mgt:swrepository}
(Month 1): 
Internal software repository.
\item
\ref{mgt:periodic-rep-1}
(Month 12): 
Project Periodic Report (first year).
\item
\ref{mgt:periodic-rep-2}
 (Month 24): 
Project Periodic Report (second year).
\item
\ref{mgt:periodic-rep-3}
(Month 36): 
Project Periodic Report (third year).
\item
\ref{mgt:final-mgt-rep}
(Month 36): 
Project Final Report
\end{compactitem}
\end{WPDeliverables}
\end{Workpackage}
